### 2025-04-01 decision-making.qmd
20250401 - median (absolute) error

ggplot2::ggplot(,
  mapping = aes(
    x = predictedValues)
) +
  geom_density(
    fill = "lightgray"
  ) +
  geom_vline(
    xintercept = mean(predictedValues),
    color = "darkgray",
    linewidth = 1.5) +
    geom_vline(
    xintercept = actualValue,
    linetype = "dashed",
    linewidth = 1.5) +
  #annotate(
  #  "segment",
  #  x = mean(predictedValues),
  #  xend = mean(predictedValues) + maeBracketingCentered_crowd,
  #  y = 0,
  #  yend = 0,
  #  linewidth = 1.5,
  #  alpha = 0.6,
  #  arrow = arrow(ends = "both")) +
  annotate(
    "text",
    x = mean(predictedValues) + (maeBracketingCentered_crowd / 2) + 1,
    y = 0.0003,
    label = paste("MAE: ", maeBracketingCentered_crowd, sep = ""),
    hjust = 0) + # left-justify
  labs(
    x = "Fantasy Points",
    y = "Density",
    title = "Density Plot of Predicted Fantasy Points for a Player",
    subtitle = "Crowd-Averaged Projection (Vertical Gray Line) Vs. Truth, i.e., Actual Fantasy Points (Dashed Line)"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

@@

ggplot2::ggplot(,
  mapping = aes(
    x = predictedValues)
) +
  geom_density(
    fill = "lightgray"
  ) +
  geom_vline(
    xintercept = mean(predictedValues),
    color = "darkgray",
    linewidth = 1.5) +
    geom_vline(
    xintercept = actualValue,
    linetype = "dashed",
    linewidth = 1.5) +
  annotate(
    "segment",
    x = mean(predictedValues),
    xend = mean(predictedValues) + maeBracketingNotCentered1_crowd,
    y = 0,
    yend = 0,
    linewidth = 1.5,
    alpha = 0.6,
    arrow = arrow(ends = "both")) +
  annotate(
    "text",
    x = mean(predictedValues) + (maeBracketingNotCentered1_crowd / 2),
    y = 0.0003,
    label = paste("MAE: ", maeBracketingNotCentered1_crowd, sep = ""),
    hjust = 0.5) + # center-justify
  labs(
    x = "Fantasy Points",
    y = "Density",
    title = "Density Plot of Predicted Fantasy Points for a Player",
    subtitle = "Crowd-Averaged Projection (Vertical Gray Line) Vs. Truth, i.e., Actual Fantasy Points (Dashed Line)"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

ggplot2::ggplot(,
  mapping = aes(
    x = predictedValues)
) +
  geom_density(
    fill = "lightgray"
  ) +
  geom_vline(
    xintercept = mean(predictedValues),
    color = "darkgray",
    linewidth = 1.5) +
    geom_vline(
    xintercept = actualValue,
    linetype = "dashed",
    linewidth = 1.5) +
  annotate(
    "segment",
    x = mean(predictedValues),
    xend = mean(predictedValues) - maeBracketingNotCentered2_crowd,
    y = 0,
    yend = 0,
    linewidth = 1.5,
    alpha = 0.6,
    arrow = arrow(ends = "both")) +
  annotate(
    "text",
    x = mean(predictedValues) - (maeBracketingNotCentered2_crowd / 2),
    y = 0.0003,
    label = paste("MAE: ", maeBracketingNotCentered2_crowd, sep = ""),
    hjust = 0.5) + # center-justify
  labs(
    x = "Fantasy Points",
    y = "Density",
    title = "Density Plot of Predicted Fantasy Points for a Player",
    subtitle = "Crowd-Averaged Projection (Vertical Gray Line) Vs. Truth, i.e., Actual Fantasy Points (Dashed Line)"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

ggplot2::ggplot(,
  mapping = aes(
    x = predictedValues)
) +
  geom_density(
    fill = "lightgray"
  ) +
  geom_vline(
    xintercept = mean(predictedValues),
    color = "darkgray",
    linewidth = 1.5) +
    geom_vline(
    xintercept = actualValue,
    linetype = "dashed",
    linewidth = 1.5) +
  annotate(
    "segment",
    x = mean(predictedValues),
    xend = mean(predictedValues) + maeNoBracketing1_crowd,
    y = 0,
    yend = 0,
    linewidth = 1.5,
    alpha = 0.6,
    arrow = arrow(ends = "both")) +
  annotate(
    "text",
    x = mean(predictedValues) + (maeNoBracketing1_crowd / 2),
    y = 0.0003,
    label = paste("MAE: ", maeNoBracketing1_crowd, sep = ""),
    hjust = 0.5) + # center-justify
  labs(
    x = "Fantasy Points",
    y = "Density",
    title = "Density Plot of Predicted Fantasy Points for a Player",
    subtitle = "Crowd-Averaged Projection (Vertical Gray Line) Vs. Truth, i.e., Actual Fantasy Points (Dashed Line)"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

ggplot2::ggplot(,
  mapping = aes(
    x = predictedValues)
) +
  geom_density(
    fill = "lightgray"
  ) +
  geom_vline(
    xintercept = mean(predictedValues),
    color = "darkgray",
    linewidth = 1.5) +
    geom_vline(
    xintercept = actualValue,
    linetype = "dashed",
    linewidth = 1.5) +
  annotate(
    "segment",
    x = mean(predictedValues),
    xend = mean(predictedValues) + maeNoBracketing2_crowd,
    y = 0,
    yend = 0,
    linewidth = 1.5,
    alpha = 0.6,
    arrow = arrow(ends = "both")) +
  annotate(
    "text",
    x = mean(predictedValues) + (maeNoBracketing2_crowd / 2),
    y = 0.0006,
    label = paste("MAE: ", maeNoBracketing2_crowd, sep = ""),
    hjust = 0.5) + # center-justify
  labs(
    x = "Fantasy Points",
    y = "Density",
    title = "Density Plot of Predicted Fantasy Points for a Player",
    subtitle = "Crowd-Averaged Projection (Vertical Gray Line) Vs. Truth, i.e., Actual Fantasy Points (Dashed Line)"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

>>>>

ggplot2::ggplot(,
  mapping = aes(
    x = predictedValues)
) +
  geom_density(
    fill = "lightgray"
  ) +
  geom_vline(
    xintercept = mean(predictedValues),
    color = "darkgray",
    linewidth = 1.5) +
    geom_vline(
    xintercept = actualValue,
    linetype = "dashed",
    linewidth = 1.5
  ) +
  #annotate(
  #  "segment",
  #  x = mean(predictedValues),
  #  xend = mean(predictedValues) + maeBracketingCentered_crowd,
  #  y = 0,
  #  yend = 0,
  #  linewidth = 1.5,
  #  alpha = 0.6,
  #  arrow = arrow(ends = "both")) +
  annotate(
    "text",
    x = mean(predictedValues) + (maeBracketingCentered_crowd / 2) + 1,
    y = 0.0003,
    label = paste("MAE: ", maeBracketingCentered_crowd, sep = ""),
    hjust = 0 # left-justify
  ) +
  labs(
    x = "Fantasy Points",
    y = "Density",
    title = "Density Plot of Predicted Fantasy Points for a Player",
    subtitle = "Crowd-Averaged Projection (Vertical Gray Line) Vs.\nTruth, i.e., Actual Fantasy Points (Dashed Line)"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

errors
median(abs(errors))
mean(predictedValues)

@@

ggplot2::ggplot(,
  mapping = aes(
    x = predictedValues)
) +
  geom_density(
    fill = "lightgray"
  ) +
  geom_vline(
    xintercept = mean(predictedValues),
    color = "darkgray",
    linewidth = 1.5) +
    geom_vline(
    xintercept = actualValue,
    linetype = "dashed",
    linewidth = 1.5
  ) +
  annotate(
    "segment",
    x = mean(predictedValues),
    xend = mean(predictedValues) + maeBracketingNotCentered1_crowd,
    y = 0,
    yend = 0,
    linewidth = 1.5,
    alpha = 0.6,
    arrow = arrow(ends = "both")
  ) +
  annotate(
    "text",
    x = mean(predictedValues) + (maeBracketingNotCentered1_crowd / 2),
    y = 0.0003,
    label = paste("MAE: ", maeBracketingNotCentered1_crowd, sep = ""),
    hjust = 0.5 # center-justify
  ) +
  labs(
    x = "Fantasy Points",
    y = "Density",
    title = "Density Plot of Predicted Fantasy Points for a Player",
    subtitle = "Crowd-Averaged Projection (Vertical Gray Line) Vs.\nTruth, i.e., Actual Fantasy Points (Dashed Line)"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

ggplot2::ggplot(,
  mapping = aes(
    x = predictedValues)
) +
  geom_density(
    fill = "lightgray"
  ) +
  geom_vline(
    xintercept = mean(predictedValues),
    color = "darkgray",
    linewidth = 1.5) +
    geom_vline(
    xintercept = actualValue,
    linetype = "dashed",
    linewidth = 1.5
  ) +
  annotate(
    "segment",
    x = mean(predictedValues),
    xend = mean(predictedValues) - maeBracketingNotCentered2_crowd,
    y = 0,
    yend = 0,
    linewidth = 1.5,
    alpha = 0.6,
    arrow = arrow(ends = "both")
  ) +
  annotate(
    "text",
    x = mean(predictedValues) - (maeBracketingNotCentered2_crowd / 2),
    y = 0.0003,
    label = paste("MAE: ", maeBracketingNotCentered2_crowd, sep = ""),
    hjust = 0.5 # center-justify
  ) +
  labs(
    x = "Fantasy Points",
    y = "Density",
    title = "Density Plot of Predicted Fantasy Points for a Player",
    subtitle = "Crowd-Averaged Projection (Vertical Gray Line) Vs.\nTruth, i.e., Actual Fantasy Points (Dashed Line)"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

ggplot2::ggplot(,
  mapping = aes(
    x = predictedValues)
) +
  geom_density(
    fill = "lightgray"
  ) +
  geom_vline(
    xintercept = mean(predictedValues),
    color = "darkgray",
    linewidth = 1.5) +
    geom_vline(
    xintercept = actualValue,
    linetype = "dashed",
    linewidth = 1.5
  ) +
  annotate(
    "segment",
    x = mean(predictedValues),
    xend = mean(predictedValues) + maeNoBracketing1_crowd,
    y = 0,
    yend = 0,
    linewidth = 1.5,
    alpha = 0.6,
    arrow = arrow(ends = "both")
  ) +
  annotate(
    "text",
    x = mean(predictedValues) + (maeNoBracketing1_crowd / 2),
    y = 0.0003,
    label = paste("MAE: ", maeNoBracketing1_crowd, sep = ""),
    hjust = 0.5 # center-justify
  ) +
  labs(
    x = "Fantasy Points",
    y = "Density",
    title = "Density Plot of Predicted Fantasy Points for a Player",
    subtitle = "Crowd-Averaged Projection (Vertical Gray Line) Vs.\nTruth, i.e., Actual Fantasy Points (Dashed Line)"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

@@

ggplot2::ggplot(,
  mapping = aes(
    x = predictedValues)
) +
  geom_density(
    fill = "lightgray"
  ) +
  geom_vline(
    xintercept = mean(predictedValues),
    color = "darkgray",
    linewidth = 1.5) +
    geom_vline(
    xintercept = actualValue,
    linetype = "dashed",
    linewidth = 1.5
  ) +
  annotate(
    "segment",
    x = mean(predictedValues),
    xend = mean(predictedValues) + maeNoBracketing2_crowd,
    y = 0,
    yend = 0,
    linewidth = 1.5,
    alpha = 0.6,
    arrow = arrow(ends = "both")
  ) +
  annotate(
    "text",
    x = mean(predictedValues) + (maeNoBracketing2_crowd / 2),
    y = 0.0006,
    label = paste("MAE: ", maeNoBracketing2_crowd, sep = ""),
    hjust = 0.5 # center-justify
  ) +
  labs(
    x = "Fantasy Points",
    y = "Density",
    title = "Density Plot of Predicted Fantasy Points for a Player",
    subtitle = "Crowd-Averaged Projection (Vertical Gray Line) Vs.\nTruth, i.e., Actual Fantasy Points (Dashed Line)"
  ) +
  theme_classic() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```
